The resevol package

### 2022-01-06 notebook/helicoverpa_notes.Rmd
Add the updates for v0.2.0.9 to the NEWS.md and notebook

@@

>>>>

 - **2022**

   - **JAN** [06](#u-06-JAN-2022)

@@

> <a name="u-06-JAN-2022">Update: 06 JAN 2022</a>

There had for some time been an annoying issue of [resevol CRAN checks](https://cran.r-project.org/web/checks/check_results_resevol.html) having ERRORs on Windows systems with ix86 architecture. As it turns out, this was caused by some errors in specifying the memory for arrays, which was fixed in [this commit](https://github.com/bradduthie/resevol/commit/b12918045402fa0a4443e4f7620d7d9d481cf3aa). Just to make sure that everything is clear and correct, I have made the cast much clearer in [a new commit](https://github.com/bradduthie/resevol/commit/223fda3cbadb79cd712b587e7153a5a7d27b71c0). Tests using the [rhub package](https://r-hub.github.io/rhub/) and on [Winbuilder](https://win-builder.r-project.org/) confirm that everything works as intended. Valgrind found no memory leaks; everything appears fine, so I have updated the version to v0.2.0.9 and submitted the fix to CRAN.
